\documentclass[line,overlapped]{res} 
\usepackage{hyperref}

\textheight=700pt

\addtolength{\topmargin}{-.4in}

\begin{document}


\name{\Huge{Kathryn M Roy}}

%-------------------------------------------------------------------------------
%   CONTACT
%-------------------------------------------------------------------------------
\noindent
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{231 Clayton Manor Dr S, Apt 3 \\}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{Liverpool, NY 13088 \\}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{(585) 755-7242}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{\href{mailto:kathrynmaeve@gmail.com}{kathrynmaeve@gmail.com}}

\begin{resume}

Dear Jason Phillips,

I am writing to apply for the Sr Software Engineer position at Dstillery, as advertised on your website. With my strong background in software engineering and my passion for innovative technologies, I am excited about the opportunity to contribute to Dstillery's mission of empowering brands and agencies with custom audience solutions.

Having visited Dstillery's website and learned about the company's commitment to leveraging data science and AI technology for programmatic advertising campaigns, I am impressed by your innovative approach and dedication to driving high-performing advertising campaigns. I am particularly drawn to Dstillery's focus on privacy-by-design solutions, such as the ID-free Custom AI™, which aligns with my belief in the importance of user privacy and data protection.

In my current role as a Software Engineer Co-Lead at Lockheed Martin, I have gained valuable experience in developing large-scale systems. I have a strong command of programming languages such as C\#, C++, and Java, and I am confident in my ability to contribute to the development of fault-tolerant systems at Dstillery. Additionally, I have experience working with technologies such as Git, JIRA, Linux, and Docker, which I believe would be valuable in collaborating with cross-functional teams and driving the successful execution of projects at Dstillery.

Beyond my technical skills and experience, I bring a strong sense of leadership and a collaborative mindset. In my current role, I have led software tasks and prioritized development efforts, ensuring successful deliveries to the customer. I am adept at working with cross-functional teams, including product managers, engineers, and stakeholders, to drive the technical direction of projects and deliver high-quality software solutions.

I am excited about the opportunity to contribute to Dstillery's growth and make a real impact in the rapidly evolving adtech industry. I have attached my resume for your review, and I would welcome the opportunity to discuss how my skills and experience align with your needs. Thank you for considering my application.

Sincerely,

Kathryn M Roy

\end{resume}
\end{document}