\documentclass[line,margin]{res} 
\usepackage{hyperref}

\textheight=700pt

\addtolength{\topmargin}{-.4in}

\begin{document}


\name{\Huge{Kathryn M Roy}}

%-------------------------------------------------------------------------------
%   CONTACT
%-------------------------------------------------------------------------------
\noindent
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{\href{https://github.com/maeve-monster}{github.com/maeve-monster\\}}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{(585) 755-7242}
\makebox[0pt][l]{}%
\makebox[\textwidth][c]{}%
\makebox[0pt][r]{\href{mailto:kathrynmaeveroy@gmail.com}{kathrynmaeveroy@gmail.com}}

\begin{resume}

%-------------------------------------------------------------------------------
%   OBJECTIVE
%-------------------------------------------------------------------------------
\section{OBJECTIVE}
A full-time job in software engineering or video game design.
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   EDUCATION SECTION
%-------------------------------------------------------------------------------
\section{EDUCATION}
\textbf{Rochester Institute of Technology}, Rochester, NY\hfill
    \textbf{2016-2020}\\
{\sl Bachelor of Science}, Video Game Design and Development.
\\
{\sl Dean's List} - Golisano College of Computing and Information Sciences:\hfill \\ Fall 2016, Spring 2017, Spring 2019
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%   TECH SKILLS SECTION
%-------------------------------------------------------------------------------
\section{COMPUTER\\SKILLS}
\textbf{Languages}: C\#, C++, Java, JavaScript, Python \\
\textbf{Other}: Git, JIRA, Linux, Jenkins, Matlab, Nodejs, DataDog, Docker
%-------------------------------------------------------------------------------
%-------------------------------------------------------------------------------
%   EXPERIENCE SECTION
%-------------------------------------------------------------------------------
\begin{format}
\title{l}\employer{r}\\
\dates{l}\location{r}\\
\body\\
\end{format}
%-------------------------------------------------------------------------------
\section{WORK EXPERIENCE}
\employer{\textbf{November 2020-Present}}
\location{Syracuse, NY}
\dates{{\sl Software Lead on Advanced Off-board Electronic Warfare (AOEW) team}}
\title{\textbf{Lockheed Martin Corporation}}
\begin{position} 
    Leadership:\\
    Led team to validate requirements for AOEW threat detection system, including final live presentation of qualification tests to the customer. \\ 
    Tracked/prioritized necessary tasks; presented to management weekly over the course of the final year of development. \\
    Delegated software development tasks to appropriate team members. \\
    On-boarded new employees and mentored interns. \\
    Participated in company sponsored STEM outreach events.\\
    \\
    Engineering:\\
    Developed Helicopter to Aircraft Carrier threat detection and defense systems in C and C++.\\
    Engineered secure data pipelines between Aircraft Carriers and Helicopters for transmission of threat detection and response information.\\
    Directed development of Java-based tools related to Helicopter and Ship emulation.\\
    Traveled to Naval bases to integrate our system into their test environment.\\
    Deployed finished software onsite and helped debug hardware issues.\\
    Performed weekly software baseline installations on prototype in lab environment.\\
    Wrote Matlab scripts for data analysis and visualization to present to stakeholders. \\
    Performed formal test procedures for the customer.
\end{position}
\employer{\textbf{January 2019-August 2019}}
\location{Rochester, NY}
\dates{{\sl Software Engineer Intern}}
\title{\textbf{Bryx}}
\begin{position}
    Built software to alert first-responders to incoming calls and related data using Kotlin and Swift.\\
    Developed pipeline to extract precise geo-coordinates from emergency calls.\\
    Designed user interface for testing geo-coding software using NodeJS.
\end{position}
\employer{\textbf{May 2018-December 2018}}
\location{Syracuse, NY}
\dates{{\sl Part-time Software Engineer}}
\title{\textbf{Lockheed Martin Corporation}}
\begin{position}
    Developed radar technology simulation testing systems using C++ and bash scripting.
\end{position}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
%   Interests
%-------------------------------------------------------------------------------
\section{ACTIVITIES}
\href{https://csh.rit.edu}{\textbf{Computer Science House}}
\hfill
\textbf{Friend of Floor}\\
A special interest house at RIT which encourages group collaboration on technical 
projects and provides access and funds to develop those projects, resources, and more\\
\textbf{Events}: 
Technical seminars, hackathons, coding competitions, tutoring\\

%\textbf{Girl Scouts} \hfill \textbf{Ambassador Level Gold Award Recipient}\\
%Created a community vegetable garden to benefit a local food cupboard.
%-------------------------------------------------------------------------------

\end{resume}
\end{document}